%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}

\begin{document}
% \header{adrien}{friggeri}
%        {social network analyst}
\header{Giuseppe}{Misurelli}{DevOps Engineer | Passionate Cyclist}

% In the aside, each new line forces a line break
\begin{aside}
  \section{Contact}
    Via Battibecco 1
    40123 Bologna
    Italy
    +39 3456353645
    +39 3383492519
    ~
    \href{mailto:giuseppe.misurelli@gmail.com}{giuseppe.misurelli@gmail.com}
    \href{https://www.strava.com/athletes/1932399}{Strava profile: Il Misu}
  \section{La Gran Cartola facts}
    120km
    2900m altitude gain
    120 riders
    14 steep climbs
    \href{https://www.facebook.com/lagrancartola/}{facebook page}
    \href{https://www.instagram.com/lagrancartola/}{\#lagrancartola}
\end{aside}

\section{Summary}

I am a passionate cyclist with over 10 years experience looking to transform my passion and hobby into a job.\par
I am currently working as a DevOps (IT) engineer for the \href{http://www.ynap.com/}{\underline{Yoox-Net-A-Porter Group}} - a leading International online luxury fashion retailer.
My day to day duties include collaborating with many different teams to gather project specific requirements and then perform automation activities to increase the system and team productivities.
Previously I worked within an E-Science European Research Project where I collaborated with many international teams across many projects.\par

I am an avid cyclist with a strong attitude at sharing my passion with new and experienced cyclists.
I have a natural attitude to establishing productive relationships as well as an intellectual curiosity for everything cycling.\par

In 2016, I started to organize and coordinate a local sportive ride to celebrate all the steep hill climbs around the metropolitan area where I live.\par
Both editions to date, have been a great opportunity for me to learn and gain experience in what it takes to organize a cycling event.

\section{Cycling experience}
Founder of \href{https://lagrancartola.tumblr.com}{\underline{La Gran Cartola}} sportive ride coordinating a staff of 12 volunteers.\\
I designed and tuned the route, completed with organizing a few test rides with local cycling clubs, organized local hosting places,
feeding zones and the final pasta party.  In order to help fund the sportive I arranged sponsorship with various companies willing to donate / help fund with promotional items.\par

During La Gran Cartola 2017, 120 riders cycled on a very tough route taking in 2900m of elevation changes over 120km’s of cycling.
In 2016 we started with 42 riders and in 2017 the event grew to over 120.\par

The event has been supported by \href{www.bandofclimbers.com}{\underline{Band of Climbers}}, who provided us with a customer designed wall poster of the famous San Luca climb in Bologna,
and \href{https://www.rapha.cc/it/it/clubhouses/milan}{\underline{Rapha Milan Clubhouse}} supplied the finisher pack to all riders who completed the event.\par

After the first edition, I started collaborating with La Gran Cartola similar events in the north of Italy creating a cycling movement and optimize event dates in a shared calendar.\par

I am a member of my cycling club coordination council managing the annual calendar of rides, events and excursions.
As part of the club events, we organize a 400km Randonnée and a vintage cycling memorial.\par

I ride between 8000 and 10000 kilometers per year (commuting, training, rides, races).\\
Among the sportive rides, my main accomplishments are:\par

\textbf{} • Tens of Audax Club Parisienne Randonneur brevets riding mostly in Italy and Germany\\
\textbf{} • Lots of Italian gran fondo successfully complete (Nove Colli and Sportful Dolomiti Race above all)\\
\textbf{} • Two times L'Eroica vintage cycling completed (130 and 205 km route)

\section{Skills}
\textbf{} • Great devotion in carrying out cycling events activities\\
\textbf{} • Self organing person and autonomous at taking decisions\\
\textbf{} • Passionate at driving the development of cycling club\\
\textbf{} • Confidence in building relationship within cycling movements\\
\textbf{} • Experience in designing cycling routes and arranging cycling events logistics

\section{Interests}
Cooking and making the traditional Bolognese pasta.\\
Dancing Lindyhop music.\\
Joining music and arts festivals.\\

\end{document}
